Members

### 2025-04-16 members.qmd
Update members.qmd with TG2 content

[Georg Heinze](https://www.meduniwien.ac.at/researcher/georg_heinze) (chair): Institute of Clinical Biometrics, Center for Medical Statistics, Informatics and Intelligent Systems, Medical University of Vienna,  Austria.

>>>>

**[Georg Heinze](https://www.meduniwien.ac.at/researcher/georg_heinze) (chair)**: Institute of Clinical Biometrics, Center for Medical Statistics, Informatics and Intelligent Systems, Medical University of Vienna,  Austria.
